RDF Constraint Types to Validate Metadata \\ on Highly-Complex Person-Level and Aggregated Data

### 2015-02-09 paper/paper7/paper7-appendix.tex
constraint type descriptions

@@

@@

@@

@@

@@

>>>>

\emph{Transitivity} is a special form of \emph{complex role inclusion}.
An \emph{object property transitivity axiom}\footnote{\emph{R-63-TRANSITIVE-OBJECT-PROPERTIES}} states that the object property is transitive — that is, if an individual \emph{x} is connected by the object property to an individual \emph{y} that is connected by the object property to an individual \emph{z}, then \emph{x} is also connected by the object property to \emph{z}.

@@

\emph{Exclusive or} is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
%In OWL 2, inclusive OR of properties would be possible to express, but not exclusive OR of data properties
Only one of multiple properties within some context (e.g. a class, a shape, or an  application profile) leads to valid data\footnote{\emph{R-11-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTIES}}.
This constraint is generally expressed in DL as follows: \ms{$C \sqsubseteq (\neg A \sqcap B) \sqcup (A \sqcap \neg B)$}.

@@

\emph{P1} is a data property (of an instance of class \emph{C1}) and its literal value must not be between the range of [$V_{min}$,$V_{max}$]\footnote{{\em R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES}}.

@@

Properties may be required\footnote{\emph{R-68-REQUIRED-PROPERTIES}}.

@@

Properties may be optional\footnote{\emph{R-69-OPTIONAL-PROPERTIES}}.

@@

Properties may be repeatable\footnote{\emph{R-70-REPEATABLE-PROPERTIES}}.
